%% Copyright 1998 Pepe Kubon
%%
%% `ack.tex' --- aknowledgments for thes-full.tex, thes-short-tex from
%%               the `csthesis' bundle
%%
%% You are allowed to distribute this file together with all files
%% mentioned in READ.ME.
%%
%% You are not allowed to modify its contents.
%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%       Acknowledgment 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\prefacesection{Acknowledgments}
First I want to thank my Ph.D. senior supervisor, Dr.~Oliver Schulte. I appreciate all his contributions of time, ideas, and funding that made my Ph.D. possible. I am very thankful for his excellent guidance, knowledge and patience throughout my Ph.D. I would also like to thank my supervisor, Dr.~Jian Pei for his guidance and support. I am grateful to Dr.~Christos Faloutsos and Dr.~David Mitchell for participating in my final defense as external and internal examiners.

I would like to  thank my family for all their love and support. I would especially  like to thank my father and mother for all the sacrifices that they have made on my behalf. And most of all I would like to thank my loving, supportive and patient husband Ali. He has been my motivation to move my career forward.

I gratefully acknowledge my collaborators and other students that I had a chance to work with during my Ph.D., Nicole Li, Zhensong Qian, Sajjad Gholami, Yan Sun and Mahmoud Khademi.

I would like to thank my friends that made my student life more enjoyable: Anahita, Elaheh, Mojtaba, Monir, Ali M., Shabnam, Atieh, Ali R. and Faezeh. 

Lastly, I would like to thank the authors whose books inspired,  entertained and educated me during my Ph.D. journey. I would like to thank Margaret Mitchell for teaching me that ``after all, tomorrow is another day''; George R.R. Martin for teaching me that ``fear cuts deeper than sword''; and Ernest Hemingway for teaching me that ``there's no one thing that's true. It's all true'.\\ 






